Behavior Driven Development in Haskell

### 2012-05-28 paper.tex
prefer "user documentation" and "code documentation" over "evidence for user" and "evidence for developer"
Need to check this again.

In BDD, all behavior should be documented, together with some
\emph{evidence}\/s for that behavior.
For this purpose, 
we brought a test method from other programming language community and
extended missing features.
In particular, we introduced Doctest~\cite{doctest} and
integrated it with QuickCheck~\cite{quickcheck}
for evidence for users.
To specify evidence for developers,
we make use of Hspec inspired by RSpec~\cite{rspec}
and we proposed some combinators to it.

@@

\noindent Note that the {\tt placeholders} library provide better keyword such as {\tt notImplemented} and {\tt todo}.
Next we write evidence for users in Haddock markup:

@@

\noindent We should execute Doctest to ensure no syntax errors.
Also, we specifies evidence for developers with Hspec:

>>>>

In BDD, all behavior should be documented, together with some
\emph{evidence}\/s for that behavior.
For this purpose, 
we brought a test method from other programming language community and
extended missing features.
In particular, we introduced Doctest~\cite{doctest} and
integrated it with QuickCheck~\cite{quickcheck}
for user documentation.
For code documentation,
we make use of Hspec inspired by RSpec~\cite{rspec}
and we proposed some combinators to it.

@@

\noindent Note that the {\tt placeholders} library provide better keyword such as {\tt notImplemented} and {\tt todo}.
Next we write user documentation in Haddock markup:

@@

\noindent We should execute Doctest to ensure no syntax errors.
Also, we write code documentation with Hspec:
